Draft_Application_Stochastic_Volatility

### 2021-07-20 Real Dataset SV.Rmd

Note that rescaling the log returns has analogous implications for the section in which we employ measures of realised volatility as a proxy for the latent volatility process.
Let us denote by $rv5_t$ the daily realised variance at time $t$, which we obtain from the \textit{rv5} series provided in the Oxford-Man database. Now, note that in a SV framework one should not directly compare $rv5_t$ to $x_t$, as $rv5_t$ can be rather seen as an estimate of the variance of the log returns at time $t$, \textit{i.e.} of $e^{x_t}$ in the SV model. Moreover, by construction of $rv5_t$,\footnote{Nota sulla formula, che considera returns, non returns in percentuale. Spiegare qui perchè possa avere senso paragonare questa varianza a quella dei log returns, come fa Guidolin} the comparison should feature a SV model where the log returns did \textit{not} undergo the percentage transformation. Thus, in order to achieve a common scale with the percentage log returns, we need to multiply $rv5$ by $100^2$. To ease the interpretation and representation of the comparison between differently approximated filtering distributions, we finally take the square root of the rescaled $rv5$, so that we compare it to $e^{x_t/2}$ (\textit{In realtà detto così è poco preciso, perchè in realtà andiamo a confrontare con la trasformazione della media dello stato filtrato}).

@@

Since we do not have access to the exact filtering distribution of the SV model, when assessing how rapidly different particle filters converge to it, we actually need to approximate even such target distribution as to have a benchmark.
Fortunately, convergence results about particle filters ensure that when the number of particles diverges, the approximation converges to the target distribution.\footnote{Bisognerebbe fare riferimento alla sezione sulla convergenza. Inoltre, va chiarito il punto della "doppia convergenza" per T e per N (ossia, se il nostro T sia sufficientemente alto da parlare già di convergenza quando N è molto grande) } Thus, we run one of the particle filters with a very large number of particles, and assume that such approximation is close enough to the target to be used itself as the target. 
With such a benchmark, we can then compare how different filters approach it as the number of particles increases. We employ the Root Mean Squared Error and the Mean Absolute Error to measure discrepancies from the benchmark. Note that the Liu and West filter can not be included in such an analysis: trivially, the comparison assumes that the competing algorithms are approximating the same target distribution.\footnote{For an analogous reason, we also conduct this analysis only on one of the three indices, the SP500. Indeed, what matters in this section is not how well the model fits the data, but rather how different algorithms approach the same distribution yielded by the same model on a given set of data.}

@@

>>>>

Note that rescaling the log returns has analogous implications for the section in which we employ measures of realised volatility as a proxy for the latent volatility process.
Let us denote by $rv5_t$ the daily realised variance at time $t$, which we obtain from the \textit{rv5} series provided in the Oxford-Man database. Now, note that in a SV framework one should not directly compare $rv5_t$ to $x_t$, as $rv5_t$ can be rather seen as an estimate of the variance of the log returns at time $t$, \textit{i.e.} of $e^{x_t}$ in the SV model.\footnote{See for example Guidolin and Pedio (2021), who employ $rv10$, another measure of realised volatility provided in the Oxford-Man Library, as a proxy for the latent conditional variance of the daily log returns on the FTSE100 index.} Moreover, by construction of $rv5_t$,\footnote{Nota sulla formula di rv5, che considera returns, non returns in percentuale.} the comparison should feature a SV model where the log returns did \textit{not} undergo the percentage transformation. Thus, in order to achieve a common scale with the percentage log returns, we need to multiply $rv5$ by $100^2$. To ease the interpretation and representation of the comparison between differently approximated filtering distributions, we finally take the square root of the rescaled $rv5$, so that we compare it to $e^{x_t/2}$.

@@

Since we do not have access to the exact filtering distribution of the SV model, when assessing how rapidly different particle filters converge to it, we actually need to approximate even such target distribution as to have a benchmark.\
Fortunately, convergence results about particle filters ensure that when the number of particles diverges, the approximation converges to the target distribution.\footnote{Molto probabilmente la frase formulata così non è formalmente corretta...bisognerebbe fare riferimento alla sezione sulla convergenza. Inoltre, va chiarito il punto della "doppia convergenza" per T e per N (ossia, se il nostro T sia sufficientemente alto da parlare di convergenza quando N è molto grande).} Thus, we run one of the particle filters with a very large number of particles, and assume that such approximation is close enough to the target to be used itself as the target.\
With such a benchmark, we can then compare how different filters approach it as the number of particles increases. We employ the Root Mean Squared Error and the Mean Absolute Error to measure discrepancies from the benchmark. Note that the Liu and West filter can not be included in such an analysis: trivially, the comparison assumes that the competing algorithms are approximating the same target distribution.\footnote{For an analogous reason, we also conduct this analysis only on one of the three indices, the SP500. Indeed, what matters in this section is not how well the model fits the data, but rather how different algorithms approach the same distribution yielded by the same model on a given set of data.}

@@

Guidolin, M., & Pedio, M. (2021). Media Attention vs. Sentiment as Drivers of Conditional Volatility Predictions: An Application to Brexit. Finance Research Letters, 101943.\
